Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Type 2R revisited

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it can be refactored. Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.
% Using this information we can determine in which locations clones are found the most, on basis of which the refactoring will be prioritized.

Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone. Therefore, we also analyze the impact of the different definitions of clone types on refactoring opportunities.
% We look at the definitions of different types of clones and the opportunities to refactor duplicate parts of code albeit not an exact match.

@@

\subsubsection{T2R clones}\label{sec:type2r}
To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce . We tackle the previously outlined shortcomings of type 2 clones to be able to detect such clones that can and should be refactored. All rules that apply to T1R clones also apply to T2R clones. Additionally, T2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold as a tradeoff exists in the refactoring of such differences. Furthermore, T2R clones allow any variability in method names and class/enum/interface names. This is because, if the body of a method/class/enum/interface equals the body of another, but only their names differ, this can be refactored without a design tradeoff.

When refactoring two fragments that differ by a few literals, called methods or used variables, we are faced with a design tradeoff. For instance, if two literals differ and we want to refactor by method extraction, we need our new method to have an added argument to which each usage can pass the literal that was used at that place. Likewise, such things can be done for different variables that have been used and different called methods. Important here is, that the type of the used literals/variables are equal. Likewise, the signature of the called methods must be equal.

@@

A method call does often not consist of a single token (unlike variables and literals). For instance, a method call \texttt{System.out.println()} consists of several segments: a type reference to the \texttt{System} type, a reference to the static \texttt{out} field and a call of the \texttt{println()} method. Because of this, T2R clones are not a subset of of type 2 clones. Because T3R clones inherit all rules of T2R clones, T3R clones are also not a subset of T3 clones. This is displayed in equation \ref{eq:typerelation2}.

\begin{equation}\label{eq:typerelation2}
T1R \subseteq T1 \text{, but } T2R	\nsubseteq T2 \text{ and } T3R \nsubseteq T3
\end{equation}

>>>>

Code clones can be found anywhere in a codebase. The location of a clone in the code has an impact on how it can be refactored. Therefore, we first look at where and how often clones can be found, enabling the prioritization of refactoring opportunities.

Furthermore, a duplicate fragment in a codebase does not always have to be an exact match with another fragment to be considered a clone. Therefore, we also analyze the impact of the different definitions of clone types on refactoring opportunities.

@@

\subsubsection{T2R clones}\label{sec:type2r}
To solve the issues identifier in Sec.~\ref{sec:type2}, we introduce an alternative definition. All rules that apply to T1R clones also apply to T2R clones. Additionally, T2R clones allow variability in literals, variables and method calls. Furthermore, T2R clones allow variability in method names and class/enum/interface names.

When refactoring two fragments that differ by literals, called methods or used variables, we are faced with a design tradeoff. When replacing the cloned fragments by a new method, we need an extra argument for each literal, called method or used variable that differs. This can be done as long as the type of used literals/variables and the signature of called methods are equal.

@@
